Computer Science House Constitution

### 2016-11-14 articles.tex
fixed some things
fixed lines and position

\asection{Appeals}
\asubsection{Executive Board Appeal}
Decisions made by the Executive Board may be appealed and overturned.
To initiate an appeal, a member must have the support of three voting members of the Executive Board, or a petition with the signatures of one-third of Active Members.
After the appeal is presented, a Simple Majority vote is held by the Executive Board whether or not to overturn and reevaluate the decision.
If the vote passes, the Executive Board may discuss and make a new ruling by another Simple Majority vote.
\asubsection{House Appeal} 
To initiate an appeal to House of an Executive Board decision, a petition with the signatures of two-thirds of Active Members must be brought to a House Meeting. After the appeal is presented and discussed, a Two-Thirds vote is held by the attending members. 
If the vote passes, attending members may discuss and make a new ruling by a Two-Thirds vote.

>>>>

\asection{Appeals}
Decisions made by the Executive Board may be appealed and overturned.
\asubsection{Executive Board Appeal}
To initiate an appeal, a member must have the support of three voting members of the Executive Board, or a petition with the signatures of one-third of Active Members.
After the appeal is presented, a Simple Majority vote is held by the Executive Board whether or not to overturn and reevaluate the decision.
If the vote passes, the Executive Board may discuss and make a new ruling by another Simple Majority vote.
\asubsection{House Appeal} 
To initiate an appeal to House of an Executive Board decision, a petition with the signatures of two-thirds of Active Members must be brought to a House Meeting. 
After the appeal is presented and discussed, a Two-Thirds vote is held by the attending members. 
If the vote passes, attending members may discuss and make a new ruling by a Two-Thirds vote.
